An elaborate data set on human gait and the effect of mechanical perturbations

### 2014-12-15 paper.tex
Added data and software availability sections, closes #70.

\section*{Processed Data}
%
We developed a toolkit for data processing,
GaitAnalysisToolKit~\cite{GATK2014}, for common gait computations and provide
an example processed trial to present the nature of the data. The tool was
developed in Python, is dependent on the SciPy Stack and Octave, and provides
two main classes: one to do basic gait data cleaning from D-Flow's output
files, \verb|DFlowData|, and a second to compute common gait variables of
interest, \verb|GaitData|.

@@

\subsection*{Author contributions}
A.v.d.B. conceived of the experiments and protocol. J.K.M and S.K.H refined the
protocol, ran the experiments, and collected the data. J.K.M was the primary
author of the paper with significant contributions from S.K.H and A.v.d.B. All
authors were involved in the revision of the draft manuscript and have agreed
to the final content.

\subsection*{Competing interests}
The authors have no  financial, personal, or professional competing interests
that could be construed to unduly influence the content of this article.

\subsection*{Grant Information}
The work was partially funded by the State of Ohio Third Frontier Commission
through the Wright Center for Sensor Systems Engineering (WCSSE).

\subsection*{Acknowledgments}
We thank Roman Boychuk and Obinna Nwanna for assistance with the experiments.

>>>>

\section*{Processed Data}
%
We developed a toolkit for data processing, GaitAnalysisToolKit v0.1.2,
\cite{Moore2014a}, for common gait computations and provide an example
processed trial to present the nature of the data. The tool was developed in
Python, is dependent on the SciPy Stack and Octave, and provides two main
classes: one to do basic gait data cleaning from D-Flow's output files,
\verb|DFlowData|, and a second to compute common gait variables of interest,
\verb|GaitData|.

@@

\section*{Data Availability}
The data set, \cite{Moore2014}, is available via the Zenodo data repository.
Two approximately 1.2GB gzipped tar balls contain the data and a \verb|README|
file with a short description of the contents. The data is released under the
Creative Commons CC0 license (http://creativecommons.org/about/cc0) following
best practices for sharing scientific data.

\section*{Software Availability}
The tables and figures in the paper can be reproduced from the source
repository shared on Github: https://github.com/csu-hmc/perturbed-data-paper.
Along with the source code in the repository, the computations depend on
version 0.1.2 of the GaitAnalysisToolKit, \cite{Moore2014a}, which can be
downloaded from Zenodo or the Python Package Index (http://pypi.python.org).

\section*{Author contributions}
A.v.d.B. conceived of the experiments and protocol. J.K.M and S.K.H refined the
protocol, ran the experiments, collected the data, developed the software, and
analyzed the data. J.K.M was the primary author of the paper with significant
contributions from S.K.H and A.v.d.B. All authors were involved in the revision
of the draft manuscript and have agreed to the final content.

\section*{Competing interests}
The authors have no financial, personal, or professional competing interests
that could be construed to unduly influence the content of this article.

\section*{Grant Information}
The work was partially funded by the State of Ohio Third Frontier Commission
through the Wright Center for Sensor Systems Engineering (WCSSE).

\section*{Acknowledgments}
We thank Roman Boychuk and Obinna Nwanna for assistance with the experiments.
